---
title: "Zillow Property Estimate Exploratory Data Analysis and Prediction"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

load the library needed for some basic data processing

```{r, message=FALSE, warning=FALSE}
library(caret)
library(data.table)
```

load the training target (logerror)
```{r}
tr_lbl = read.csv("D:\\Kaggle\\Zestimate\\train_2016_v2.csv")
tr_lbl = tr_lbl[order(tr_lbl$parcelid),]
```

load the training data set

```{r, message=FALSE, warning=FALSE}
tr_data = fread("D:\\Kaggle\\Zestimate\\properties_2016.csv")
```
merge the training data with the corresponding labels using the parcelid as the key
```{r, message=FALSE, warning=FALSE}
mergedData = merge(tr_lbl, tr_data, by="parcelid")
attach(mergedData)
```

plot logerror against year built
```{r, message=FALSE, warning=FALSE}
data = data.frame(cbind(yearbuilt, abs(logerror)))
data_agg = aggregate(data, by=list(data$yearbuilt), FUN=mean)
data_agg = data_agg[,-1]
plot(data_agg$yearbuilt, data_agg$V2, type = "l")
```
the logerror tends to be higher for homes built before the 1900s.

Calculate fraction of missing values per feature
```{r, message=FALSE, warning=FALSE}
NAcount_ratio = sapply(tr_data, function(x) sum(is.na(x))/length(x))
NAcount_ratio = NAcount_ratio[order(NAcount_ratio)]
barplot(NAcount_ratio, las=2, main="NAs per feature")
```

how many samples do we have for each month?
```{r, message=FALSE, warning=FALSE}
tr_lbl$transactiondate = as.Date(tr_lbl$transactiondate)
month = format(tr_lbl$transactiondate, "%m")
hist(as.numeric(month), xlab = "Month")
```


Does absolue log error vary by month?
```{r, message=FALSE, warning=FALSE}
err_by_month = data.frame(tr_lbl[,-c(1,3)])
err_by_month$month = month
colnames(err_by_month) = c("logerror", "month")
err_by_month$logerror=abs(err_by_month$logerror)

mean_logE_by_month = aggregate(err_by_month, by=list(err_by_month$month), FUN = mean)
plot(mean_logE_by_month$Group.1, mean_logE_by_month$logerror, type="l", xlab = "Month", ylab="mean abs logerror")
```





## Zillow Estimate Error Prediction
For the prediction code please visit this page: https://github.com/hadi-android/Kaggle-Property-Estimate/blob/master/code_xgboost.R

